R tools for accessing research literature for text mining

### 2019-08-23 manuscript.Rmd

Fatcat is a project from Ben Newbold of the Internet Archive Labs. It is a
"versioned, publicly-editable catalog of research publications:  journal articles,
conference proceedings, preprints, blog posts". Fatcat is currently does not have an
R client, but is used inside of the [fulltext][] package.

>>>>

Fatcat is a project from Ben Newbold of the Internet Archive Labs. It is a
"versioned, publicly-editable catalog of research publications:  journal articles,
conference proceedings, pre-prints, blog posts". Fatcat currently does not have an
R client, but is used inside of the [fulltext][] package.

### 2019-08-23 manuscript.tex

There's more than 100 million research articles published (Crossref API:
\url{https://github.com/CrossRef/rest-api-doc}), representing an
enormous amount of knowledge. In addition to simply reading these
articles, the articles contain a vast trove of information of interest
to researchers for machine aided questions (Kong \& Gerstein, 2018; Usai
et al., 2018). For example, many researchers are interested in
statistical outcomes of articles that can be extracted from numeric
results: P-values, effect sizes, means, and more. In addition,
researchers are often interested in words in articles, their use through
time, and the contexts they are found in.

>>>>

There are more than 100 million research articles published (Crossref
API: \url{https://github.com/CrossRef/rest-api-doc}), representing an
enormous amount of knowledge. In addition to simply reading these
articles, the articles contain a vast trove of information of interest
to researchers for machine aided questions (Kong \& Gerstein, 2018; Usai
et al., 2018). For example, many researchers are interested in
statistical outcomes of articles that can be extracted from numeric
results: P-values, effect sizes, means, and more. In addition,
researchers are often interested in words in articles, their use through
time, and the contexts they are found in.

### 2019-08-23 use-cases/full-text-mining.Rmd

>>>>

_Further processing_

From here, you'll likely want to use R packages for removing stopwords, tokenizing, 
and more. The Natural Language Processing CRAN Task View
(https://cloud.r-project.org/web/views/NaturalLanguageProcessing.html) is a good place
to start if you're not sure what packages to use. Some packages worth trying in this
space are [antiword][], [pdftools][], [rtika][], [tokenizers][], and [textreuse][].

[antiword]: https://github.com/ropensci/antiword
[pdftools]: https://github.com/ropensci/pdftools
[rtika]: https://github.com/ropensci/rtika
[tokenizers]: https://github.com/ropensci/tokenizers
[textreuse]: https://github.com/ropensci/textreuse
